\thesistitle

### 2019-08-19 icse/paper.tex
Vashisht
JDeodorant progress

\subsection{Allowing variability in a controlled set of expressions} \label{sec:t2r}
%Explain type 2, why it is not always refactorable, solution
Often, duplication fragments in source code do not match exactly \cite{kodhai2013method}. Often when developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose. To detect duplicate fragments with minor variance, we looked into in what expressions we can allow variability while still being refactorable.

We define the following expressions as refactorable when varied:
\begin{itemize}
  \item \textbf{Literals}: Only if all varying literals in a clone class have the same type.
  \item \textbf{Variables}: Only if all varying variables in a clone class have the same type.
  \item \textbf{Method references}: Only if the return value of referenced methods match (or are not used).
\end{itemize}
Often when allowing such variance, trade-offs come into play. For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code.

\subsection{Gapped clones} \label{sec:t3r}
%Explain type 3, why it is not always refactorable, solution
Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context \cite{roy2007survey}. When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones'' \cite{ueda2002detection, zhao2018automatic}. ``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s). We define the following methods to refactor such clones:
\begin{itemize}
  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
  \item We use a lambda function to pass the difference in statements from each location of the clone.
\end{itemize}
For both refactoring techniques a trade-off is at play, as these solutions increase the complexity and volume of the source code in favor of removing a clone.

\section{CloneRefactor}
% NEED TO EXPLAIN WHY DO CURRENT DETECTION TOOLS NOT SUFFICE
% The tool: Detect Clones, Map Context, Refactor.
To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques \cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}. We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output. None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing} seemed suitable, because of which we decided to implement our own tool.

>>>>

\subsection{Allowing variability in a controlled set of expressions} \label{sec:t2r}
%Explain type 2, why it is not always refactorable, solution
Often, duplication fragments in source code do not match exactly \cite{kodhai2013method}. Often when developers duplicate fragments of code, they modify the duplicated block to fit its new location and purpose. To detect duplicate fragments with minor variance, we look into in what expressions we can allow variability while still being refactorable.

We define the following expressions as refactorable when varied:
\begin{itemize}
  \item \textbf{Literals}: Only if all varying literals in a clone class have the same type.
  \item \textbf{Variables}: Only if all varying variables in a clone class have the same type.
  \item \textbf{Method references}: Only if the return value of referenced methods match (or are not used).
\end{itemize}
Often when allowing such variance, trade-offs come into play \cite{krishnan2013refactoring, krishnan2014unification}. For instance, variance in literals may require the introduction of a parameter to an extracted method if the ``Extract Method'' refactoring method is used, increasing the required effort to comprehend the code.

\subsection{Gapped clones} \label{sec:t3r}
%Explain type 3, why it is not always refactorable, solution
Sometimes, when fragments are duplicated, a statement is inserted or changed severely for the code to fit its new context \cite{roy2007survey}. When dealing with such a situation, there are several opportunities to refactor so-called ``gapped clones'' \cite{ueda2002detection, zhao2018automatic}. ``Gapped clones'' are two clone instances separated by a ``gap'' of non-cloned statement(s). We define the following methods to refactor such clones:
\begin{itemize}
  \item We wrap the difference in statements in a conditionally executed block, one path for each different (group of) statement(s).
  \item We use a lambda function to pass the difference in statements from each location of the clone \cite{tsantalis2017clone}.
\end{itemize}
For both refactoring techniques a trade-off is at play, as these solutions increase the complexity and volume of the source code in favor of removing a clone.

\section{CloneRefactor}
% NEED TO EXPLAIN WHY DO CURRENT DETECTION TOOLS NOT SUFFICE
% The tool: Detect Clones, Map Context, Refactor.
To detect such clones that can be refactored, we surveyed a set of modern clone detection tools and techniques \cite{svajlenko2014evaluating, sheneamer2016survey, gautam2016various, roy2009comparison}. We created a set of control projects to determine the suitability of these tools to detect refactorable clones, either through configuration or postprocessing of their output. None of the surveyed tools \cite{ragkhitwetsagul2019siamese, roy2008nicad, semura2017ccfindersw, sajnani2016sourcerercc, saini2018oreo, jiang2007deckard, kamalpriya2017enhancing, mazinanian2016jdeodorant} were suitable with our findings about refactorable clones, because of which we decided to implement our own tool.

### 2019-08-19 sections/related_work.tex
JDeodorant progress

\subsection{JDeodorant}
\cite{krishnan2013refactoring, krishnan2014unification, tsantalis2015assessing, mazinanian2016jdeodorant, tsantalis2017clone}
\todo{TODO}

>>>>

\subsection{JDeodorant}
The most used tool used to help in the process of refactoring clones is JDeodorant \cite{mazinanian2016jdeodorant}. This tool is based on a set of studies, that look into several aspects of the clone refactoring process. The first of these studies is ``Refactoring Clones: An Optimization Problem'' by Krishnan et al.~\cite{krishnan2013refactoring}. The authors describe clones that are refactored by extracting their functionality to a single method. They also describe that variability between identifiers and literals have to become parameters in the extracted method. They identify the optimization problem where the variability between cloned fragments should be limited, to avoid limiting the reusability of methods because of too many method parameters. They propose an algorithm that calculates the variance between code fragments on basis of the difference in AST nodes.

The second study, ``Unification and Refactoring of Clones'' by Krishnan et al.~\cite{krishnan2014unification}, the authors address the problem of the modifications made to copied fragments and their impact on the refactoring process. They identify a list of expressions in which they have found variability, which is displayed in Table~\ref{tab:krishnanvariability}.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lcc@{}}
\toprule
\textit{\textbf{Difference Type}} & \multicolumn{2}{c}{\textit{\textbf{Example}}}                                                \\ \midrule
Variable Identifier               & \multicolumn{1}{c|}{\texttt{int x = \textbf{y};}}       & \texttt{int x = \textbf{z};}       \\
Literal Value                     & \multicolumn{1}{c|}{\texttt{String s = \textbf{"s1"};}} & \texttt{String s = \textbf{"s2"};} \\
Method Name                       & \multicolumn{1}{c|}{\texttt{expr.\textbf{foo}(arg);}}   & \texttt{expr.\textbf{bar}(arg);}   \\
Argument Number                   & \multicolumn{1}{c|}{\texttt{foo(\textbf{arg0, arg1});}} & \texttt{foo(\textbf{arg0});}       \\
Caller Expression                 & \multicolumn{1}{c|}{\texttt{\textbf{expr.}foo(arg);}}   & \texttt{foo(arg);}                 \\
Array Dimension                   & \multicolumn{1}{c|}{\texttt{int x = a\textbf{[i]};}}    & \texttt{int x = a\textbf{[i][j]};} \\
AST Compatible                    & \multicolumn{1}{c|}{\texttt{int x = \textbf{foo()};}}   & \texttt{int x = \textbf{5};}       \\ \midrule
Operator                          & \multicolumn{1}{c|}{\texttt{int x = y \textbf{+} z;}}   & \texttt{int x = y \textbf{-} z;}   \\
Variable Type                     & \multicolumn{1}{c|}{\texttt{\textbf{int} x = 5;}}       & \texttt{\textbf{double} x = 5;}    \\ \bottomrule
\end{tabular}%
}
\caption{Expression variability table from Krishnan et al.~\cite{krishnan2014unification}}
\label{tab:krishnanvariability}
\end{table}

\cite{krishnan2013refactoring, krishnan2014unification, tsantalis2015assessing, mazinanian2016jdeodorant, tsantalis2017clone}
\todo{TODO}
